High-order cognition is supported by complex but compressible brain activity patterns

### 2023-02-28 paper/main.tex
checking in draft of results section, added new discussion figure

\newcommand{\synthThirds}{S1}

@@

@@

@@

>>>>

\newcommand{\synthThirds}{S1}
\newcommand{\accuracyNetworks}{S2}
\newcommand{\componentsNetworks}{S3}

@@

We also wondered how informativeness and compressibility in the different
experimental conditions might vary across brain networks. We used a network
parcellation identified by \cite{YeoEtal11} to segment the brain into seven
distinct networks. The networks can be sorted (roughly) in order from
lower-level to higher-level cortex as follows (Fig.~\ref{fig:networks}A):
visual, somatomotor, dorsal attention, ventral attention, limbic,
frontoparietal, and default mode. Next, we computed decoding curves separately
for the activity patterns within each network and identified each network's
inflection point, for each experimental condition. Moving from low-order
networks to higher-order networks, we found that decoding accuracy (for the
intact condition) tended to increase
(Figs.~\ref{fig:networks}B,~\accuracyNetworks). This suggests that higher-order
networks may carry more content-relevant or stimulus-driven ``information.'' We
found no clear trends in the numbers of components at each network's inflection
point across networks or conditions
(Figs.~\ref{fig:networks}C,~\componentsNetworks). \textbf{JRM NOTE: expand on
this once we have the new figures.}

@@

In addition to examining different networks in isolation, we wondered about the
general structure of the full-brain (i.e., potentially multi-network) activity
patterns reflected by different principal components across different
experimental conditions. Figure~\ref{fig:neurosynth-pca} displays inflated
brain maps of the top five highest-weighted components, for each experimental
condition. We also used Neurosynth~\citep{RubiEtal17} to identify, for each
component, the top five terms associated with each map (see \textit{Reverse
inference}). We noticed (by inspection) several common themes across the sets
of terms associated with each component and condition. Memory-related
components included terms like ``middle temporal,'' ``memory retrieval,'' and
``working memory.'' Sensory processing related components included terms like
``primary visual,'' ``auditory cortex,'' ``v1,'' and so on. Other components
were associated with sensory integration (e.g., ``thalamic,'' ``cingulate,''
etc.), sentence comprehension (e.g., ``sentence,'' ``comprehension''), emotion
and valence (e.g., ``amygdala,'' ``valance''), or the default mode network
(e.g., ``default mode'').  The components we identified were relatively stable
across story segments (Fig.~\synthThirds).

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/discussion}

\caption{\textbf{Summary of functions associated with top-weighted components
by condition.} Each column corresponds to an experimental condition. Brain maps
in the top row are reproduced from Figure~\ref{fig:neurosynth-pca}, for
reference. Cognitive functions summarized from the top Neurosynth-derived terms
in Figure~\ref{fig:neurosynth-pca} are listed in the rows on the left.  Shaded cells
denote which experimental conditions were associated with one or more top-weighted
principal components associated with the given function.}

\label{fig:discussion}
\end{figure}
